\textit{Supplementary materials for}: Text embedding models reveal high resolution insights into conceptual knowledge from short multiple choice quizzes

### 2023-01-26 paper/supplement.tex
flattened transparency in Fig 1, lots of minor wording tweaks, added a topic comparison figure + associated text to the results section

\newcommand{\demo}{1}

\title{\textit{Supplementary materials for}: Geometric models reveal the hidden structure of conceptual knowledge}

@@

\newpage
\renewcommand{\refname}{Supplementary references}
\bibliographystyle{apa}
\bibliography{CDL-bibliography/cdl}

>>>>

\newcommand{\knowledgeMaps}{5}

\title{\textit{Supplementary materials for}: Text embedding models reveal high
resolution insights into conceptual knowledge from short multiple choice
quizzes}

@@

\begin{figure}[tp]
    \centering
    \includegraphics[height=0.9\textheight]{figs/individual-knowledge-maps-quiz1}

    \caption{\textbf{Individual participants' knowledge maps estimated from
    Quiz 1 responses.} Each panel is in the same format as the knowledge maps
    displayed in the left panel of Figure~\knowledgeMaps A in the main text,
    but here the maps have been computed separately for each participant.}

    \label{fig:knowledge-maps-q1}
\end{figure}

\begin{figure}[tp]
    \centering
    \includegraphics[height=0.9\textheight]{figs/individual-knowledge-maps-quiz2}

    \caption{\textbf{Individual participants' knowledge maps estimated from
    Quiz 2 responses.} Each panel is in the same format as the knowledge maps
    displayed in the middle panel of Figure~\knowledgeMaps A in the main text,
    but here the maps have been computed separately for each participant.}

    \label{fig:knowledge-maps-q2}
\end{figure}

\begin{figure}[tp]
    \centering
    \includegraphics[height=0.9\textheight]{figs/individual-knowledge-maps-quiz3}

    \caption{\textbf{Individual participants' knowledge maps estimated from
    Quiz 3 responses.} Each panel is in the same format as the knowledge maps
    displayed in the right panel of Figure~\knowledgeMaps A in the main text,
    but here the maps have been computed separately for each participant.}

    \label{fig:knowledge-maps-q3}
\end{figure}

\begin{figure}[tp]
    \centering
    \includegraphics[height=0.9\textheight]{figs/individual-learnings-maps-quiz1-2}

    \caption{\textbf{Individual participants' learning maps estimated from
    Quiz 1 and 2 responses.} Each panel is in the same format as the learning map
    displayed in the left panel of Figure~\knowledgeMaps B in the main text,
    but here the maps have been computed separately for each participant.}

    \label{fig:learning-maps-q1_2}
\end{figure}

\begin{figure}[tp]
    \centering
    \includegraphics[height=0.9\textheight]{figs/individual-learnings-maps-quiz2-3}

    \caption{\textbf{Individual participants' learning maps estimated from
    Quiz 2 and 3 responses.} Each panel is in the same format as the learning map
    displayed in the right panel of Figure~\knowledgeMaps B in the main text,
    but here the maps have been computed separately for each participant.}

    \label{fig:learning-maps-q1_2}
\end{figure}

\renewcommand{\refname}{Supplementary references}
\bibliographystyle{apa}
\bibliography{CDL-bibliography/cdl}
